Bayesian estimation of chronic disease epidemiology from incomplete data

### 2021-07-01 metahit/paper_analyses.Rmd
A range of doc and code fixes

@@

pdf("../write/all_cf_indep.pdf",width=6,height=6)

gg <- resall %>% 
  dplyr::filter(model %in% c("Independent areas","National"), var=="cf") %>%
  mutate(p50 = 1 - exp(-`50%`),
         plow = 1 - exp(-`2.5%`),
         pupp = 1 - exp(-`97.5%`)) %>%
  ggplot(aes(x=age, y=p50, group=area)) + 
  geom_ribbon(aes(ymin=plow, ymax=pupp), 
              fill="deepskyblue") +
  geom_line() + 
  facet_grid(cols=vars(gender), rows=vars(disease), scales = "free_y", switch = "y") + 
  xlab("Age (years)") + 
  ylab("Annual case fatality probability") + 
  xlim(60,100) + 
  theme(strip.text.y.left = element_text(angle = 0))

>>>>

res %>% filter(disease=="Uterine cancer", var=="cf", between(age, 58, 70))
res_utrc %>% filter(disease=="Uterine cancer", var=="cf", between(age, 90, 100))
## Smoothed hasn't worked

@@

pdf("../../write/all_cf_indep.pdf",width=6,height=6)

gg <- resall %>% 
  dplyr::filter(model %in% c("Independent areas","National"), var=="cf") %>%
  dplyr::filter(! (disease=="Uterine cancer" & age > 90)) %>%
  mutate(p50 = 1 - exp(-`50%`),
         plow = 1 - exp(-`2.5%`),
         pupp = 1 - exp(-`97.5%`)) %>%
  ggplot(aes(x=age, y=p50, group=area)) + 
  geom_ribbon(aes(ymin=plow, ymax=pupp), 
              fill="deepskyblue") +
  geom_line() + 
  facet_grid(cols=vars(gender), rows=vars(disease), scales = "free_y", switch = "y") + 
  xlab("Age (years)") + 
  ylab("Annual case fatality probability") + 
  xlim(60,100) + 
  theme(strip.text.y.left = element_text(angle = 0))
